Short and Mechanized Logical Relation for Dependent Type Theory

### 2024-02-23 paper/paper.tex
another comment

@@

To state the adequacy lemma, we first define the notion
of reducibility candidates (shortened as $CR$), predicates over sets
of lambda terms that capture the properties we need from our logical
relation.
\begin{definition}[CR]
  Let $[[S]]$ be a set of lambda terms. We say that
  \begin{itemize}
  \item $[[S]] \in CR_1 \iff $  $[[forall a, (#  wne a implies a in S #)]]$
  \item $[[S]] \in CR_2 \iff$ $[[forall a, (# a in S implies wn a #)]]$
  \item $[[S]] \in CR \iff $ $[[S]] \in CR_1$ and $[[S]] \in CR_2$
  \end{itemize}
\end{definition}

@@

Autosubst 2 takes our syntax specification in higher-order abstract
syntax and generates Coq syntax specification, renaming and
substitution functions, and lemmas and tactics that allow reasoning
about those functions. The auto-generated files and the library header
files are counted toward the \emph{Library (Autosubst 2)} category.

>>>>

\scw{The goal of this section is also to demonstrate that our logical relations 
  proof technique can be extended to reason about the (parallel) reduction of 
  open terms, not just the reduction of terms after closing 
  substitutions. This is important, in particular, for dependently-typed languages 
  because type checking involves reasoning about open terms. But even simple type 
  systems may wish to employ this sort of reasoning, in the case of, say, reasoning 
  about compiler correctness in open environments. (Does Amal do anthing like this?)
}

@@

To state the adequacy lemma, we first define the notion
of reducibility candidates (shortened as $CR$), predicates over sets
of lambda terms that capture the properties we need from our logical
relation. \scw{Need to provide intuition for these two properties that need 
to be proved similtaneously. Also, cite where this form of proof originally 
appeared? This part is standard.}
\begin{definition}[CR]
  Let $[[S]]$ be a set of lambda terms. We say that
  \begin{itemize}
  \item $[[S]] \in CR_1 \iff $  $[[forall a, (#  wne a implies a in S #)]]$
  \item $[[S]] \in CR_2 \iff$ $[[forall a, (# a in S implies wn a #)]]$
  \item $[[S]] \in CR \iff $ $[[S]] \in CR_1$ and $[[S]] \in CR_2$
  \end{itemize}
\end{definition}

@@

Autosubst 2 takes our syntax specification in higher-order abstract
syntax and generates Coq syntax specification, renaming and
substitution functions, and lemmas and tactics that allow reasoning
about those functions. The auto-generated files and the library header
files are counted toward the \emph{Library (Autosubst 2)} category.
\scw{this line is no longer in the figure}
